Evolution of Processes in Delivering Reliable Software within the European Scientific Arena

### 2019-02-13 paper-jgc.tex
Rephrase to refer INDIGO as a concluded project

The {\sl INDIGO--DataCloud} (INtegrating Distributed data Infrastructures for Global
explOitation, Apr 2015 -- Sep 2017) \cite{cordis:indigo} is the last
project of software development considered in this paper. At the time of writing,
the project is succeeding in providing solutions to address the existing gaps in
Cloud Platform--as--a--Service (PaaS) and Software--as--a--Service (SaaS) levels,
helping developers, e--Infrastructure administrators and scientific communities to exploit
Cloud computing benefits.

>>>>

The {\sl INDIGO--DataCloud} (INtegrating Distributed data Infrastructures for Global
explOitation, Apr 2015 -- Sep 2017) \cite{cordis:indigo} is the last
project of software development considered in this paper. The project addressed
the existing gaps at the Cloud Platform--as--a--Service (PaaS) and Software--as--a--Service (SaaS) levels,
helping developers, e--Infrastructure administrators and scientific communities to exploit
Cloud computing benefits.
